Clustering in a hyperbolic model of complex networks.

### 2019-02-28 clustering_infinite_model.tex
typos in section 3

$$ \mu(y) = \mu(p) := \mu(\BallPo{p}). $$
Integrating the intensity function of $\Pcal$ over $\BallPo{p}$ gives

@@

where $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$. 
We will often write $\rho(y,k)$ instead of $\rho(p,k)$.

Let the random variable $D$ denote the degree of the typical point.
Since the typical point has a height that is independent of the Poisson process and exponential($\alpha$)-distributed:
\begin{equation}\label{eq:def_pk}
	p_k := \Pee( D=k ) = \int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \, dy.
\end{equation}

@@

Let the random variable $C$ denote the clustering coefficient of the typical point $(0,y)$, in the graph obtained from $\Ginf$ by adding $(0,y)$. We {\em define}
\[
	\gamma := \Ee C, \quad \gamma(k) := \Ee\left( C | D = k \right).
\]
(Where we take the expection over both the Poisson point process $\Pcal$ and $y \isd \text{exp}(\alpha)$, independent of the Poisson process $\Pcal$.) We shall show shortly that these take on the values stated in Theorem~\ref{thm:maincc} and~\ref{thm:mainkfixed}.

For any fixed value $y_0>0$, the set of points inside $\BallPo{(0,y_0)}$ is a Poisson process with intensity $f \cdot 1_{\BallPo{(0,y_0)}}$. As $\mu(\BallPo{(0,y_0)}) = \mu(y_0) = \xi e^{y_0/2} < \infty$, this can be described alternatively by the experiment where we first pick $N \isd \Po( \mu(y_0) )$ then and we take $N$ i.i.d.~points in $\BallPo{(0,y_0)}$ according to the probability density $f \cdot 1_{\BallPo{(0,y_0)}} / \mu(y_0)$. (That is, the intesity function of the Poisson point process, but set to zero outside of $\BallPo{(0,y_0)}$ and renormalized in such a way that it integrates to one.) Hence, if we condition on the event that $y$ takes on some fixed value $y_0$ and that there are exactly $k$ points of $\Pcal$ inside $\BallPo{(0,y_0)}$, then those $k$ points behave like $k$ i.i.d.~points in $\BallPo{(0,y_0)}$ chosen according to the mentioned renormalized probability density function. This shows that, for every $k\geq 2$:
\[
	\Ee\left( C | D=k, y=y_0 \right) 
	= \frac{1}{{k\choose 2}} \Ee\left( \sum_{1\leq i < j \leq k} 1_{\{u_i\in \BallPo{u_j}\}} \right)
	= \Exp{1_{\{u_1\in\BallPo{u_2}\}}},
\]
where $u_1,\dots, u_n$ are i.i.d.~points in $\BallPo{(0,y_0)}$ with the above mentioned density.
Note that this does not depend on the value of $k$. For notational convenience, we'll write 
\[ 
	P(y_0) := \Exp{1_{\{u_1\in\BallPo{u_2}\}}},
\]
with $u_1, u_2$ as above.

@@

Recall that $P(y_0)$ is the probability that $u_1 = (x_1,y_1), u_2 = (x_2,y_2)$ are neighbours in $\Ginf$, where
$u_1, u_2$ are i.i.d.~with probability density $f \cdot 1_{\BallPo{(0,y_0)}} / \mu(y_0)$.
In particular

$$ \begin{array}{rcl} 
\Pee( y_i > t ) 
& = & 
\frac{\nu\alpha}{\pi \mu(y_0)} \int_t^\infty \int_{-e^{(s+y_0)/2}}^{e^{(s+y_0)/2}} e^{-\alpha s}\, d s \\
& = & 
\frac{\nu\alpha}{\pi \mu(y_0)} \int_t^\infty 2 e^{(s+y_0)/2} \cdot e^{-\alpha s}\, d s \\
& = & 
\frac{2 \nu\alpha e^{y_0/2} }{\pi \xi e^{y_0/2} (\alpha-\frac12) }  \cdot e^{(\frac12-\alpha)t} \\
& = & 
 e^{(\frac12-\alpha)t},
\end{array} $$

@@

\begin{lemma}\label{lem:triangle_prob_y_coordinates}
\begin{align*}
P(y_0(z_0),y_1(z_1),y_2(z_2)) = \begin{cases}
	1 &\text{ if } z_0 \geq z_1+z_2, z_0 > z_1 > z_2, \\
	1-G(z_0,z_1,z_2) &\text{ if } z_0 < z_1+z_2, z_0 > z_1 > z_2, \\
	\frac{z_0}{z_1} &\text{ if } z_1 \geq z_0+z_2, z_1 > \max(z_0,z_2), \\
	\frac{z_0}{z_1}\left(1-G(z_1,z_0,z_2)\right) &\text{ if } z_1 < z_0+z_2, z_1 > \max(z_0,z_2),
\end{cases}
\end{align*}
where 
\begin{align*}
G(a,b,c) = \frac{1}{4}
\left( b^{-1}c + bc^{-1} + a^2b^{-1}c^{-1} + 2 - 2ab^{-1}-2ac^{-1}\right)
\end{align*}
\end{lemma}

@@

\begin{proof}
Note that $P(y_0,y_1,y_2)$ is the probability that $x_2$ falls into the interval $[x_1-e^{(y_1+y_2)/2},x_1+e^{(y_1+y_2)/2}]$ , as well as into the interval $[-e^{(y_0+y_2)/2},e^{(y_0+y_2)/2}]$. By symmetry considerations, we can take $x_1$ uniformly at random from $[0,e^{y_0/2+y_1/2}]$ as opposed to $[-e^{y_0/2+y_1/2}, e^{y_0/2+y_1/2}]$. Figure~\ref{fig:triangle_prob_lemma} show the intersection of the intervals (red line) for two different cases for $x_1 \le e^{(y_0 + y_1)/2}$.

@@

We now conclude that
\[
	P(y_0(z_0), y_1(z_1), y_2(z_2)) = 1 \quad \text{if} \quad z_0 > z_1 > z_2 \text{ and } z_0 \geq z_1 + z_2
\]
while for $z_0 > z_1 > z_2$ and $z_0 < z_1 + z_2$
\begin{align*}
	P(y_0, y_1, y_2) 
	&= 1 - \frac{z_0^2z_1z_2}{4} \cdot \left( z_0^{-1}z_1^{-1}+z_0^{-1}z_2^{-1}-z_1^{-1}z_2^{-1} \right)^2 \\
%	&= 1 - \frac{z_0^2z_1z_2}{4} \cdot \left( z_0^{-2}z_1^{-2} + z_0^{-2}z_2^{-2} + z_1^{-2}z_2^{-2}
%		+ 2z_0^{-2}z_1^{-1}z_2^{-1} - 2 z_0^{-1}z_1^{-2}z_2^{-1} - 2z_0^{-1}z_1^{-1}z_2^{-2} \right) \\
	&= 1 - \frac{1}{4} \left( z_1^{-1}z_2 + z_1z_2^{-1} + z_0^2z_1^{-1}z_2^{-1} + 2 - 2z_0z_1^{-1}-2z_0z_2^{-1}\right),
\end{align*}
which finishes the proof.
\end{proof}

@@

\begin{proof}[Proof of Lemma~\ref{lem:triangle_prob_y_coordinates}]
Let $y_i >0$ and $z_i = e^{-y_i/2}$, $i=0,1,2$. Lemma~\ref{lem:ordered} gives the expression for $P(y_0(z_0),y_1(z_1),y_2(z_2))$ in the case $y_0<y_1<y_2$, or equivalently $z_0>z_1>z_2$, i.e. the first two lines in the claim of Lemma~\ref{lem:triangle_prob_y_coordinates}. To analyze the other cases we shall express $P(y_1,y_0,y_2)$ and $P(y_1,y_2,y_0)$ in terms of $P(y_0,y_1,y_2)$ and $z_i$. For this we note that we can view $P(y_0,y_1,y_2)$ as a 2-fold integral of the indicator function
\[ 
	h(x_0, x_1, x_2) := \ind{ |x_0 - x_1| < e^{(y_0+y_1)/2}, |x_0 - x_2| < e^{(y_0+y_2)/2}, |x_1-x_2| < e^{(y_1+y_2)/2}}, 
\]
where $x_0$ was set to zero, without loss of generality, and the other two $x_i$ are uniform random variables on $[-e^{(y_0)+y_i)/2}, e^{(y_0+y_i)/2}]$. When we consider the probability $P(y_1,y_0,y_2)$, this is the 2-fold integral of $h(x_0,0,x_2)$ so that
\begin{align*}
	P(y_1,y_0,y_2) &= \frac{1}{2e^{(y_1+y_0)/2}} \cdot \frac{1}{2e^{(y_1+y_2)/2}} 
		\iint_{\R} h(x_0,0,x_2) \dd x_0 \dd x_2\\
	&= \frac{e^{y_0/2}}{e^{y_1/2}} \frac{1}{2e^{(y_0+y_1)/2}} \frac{1}{2e^{(y_0+y_2)/2}} 
		\iint_{\R} h(0,x_1,x_2) \dd x_1 \dd x_2\\
	&= \frac{e^{y_0/2}}{e^{y_1/2}} P(y_0,y_1,y_2) = \frac{z_1}{z_0}  P(y_0,y_1,y_2).
\end{align*}
Finally we note that $h(x_0,0,x_2) = h(x_2,0,x_0)$ from which we conclude that
\begin{equation}\label{eq:symmetry_relation_triangle_prob}
	P(y_0, y_1, y_2) = \left(z_0/z_1\right) P(y_1,y_0,y_2) = \left(z_0/z_1\right) P(y_1,y_2,y_0).
\end{equation}

@@

Applying the change of variables $z_i := e^{-y_i/2}$ and Lemma~\ref{lem:triangle_prob_y_coordinates} gives %${\dd}y_i = -\frac{2{\dd}z_i}{z_i}$ and therefore
\begin{align*}
	I_1(y_0) &=	4 (\alpha-1/2)^2 \cdot \int_{z_0>z_1>z_2>0} P(y_0,y_1(z),y_2(z)) z_1^{2\alpha-2} z_2^{2\alpha-2} 
		{\dd}z_2{\dd}z_1 \\
	&= 4 (\alpha-1/2)^2 \cdot \left( \int_{z_0>z_1>z_2>0} 1 \cdot z_1^{2\alpha-2} z_2^{2\alpha-2} 
		{\dd}z_2{\dd}z_1 \right. \\
	&\hspace{10pt} \left. - \int_{{z_0>z_1>z_2>0,}\atop{z_0 < z_1+z_2}} G(z_0,z_1,z_2) \cdot z_1^{2\alpha-2} z_2^{2\alpha-2} 
		{\dd}z_2{\dd}z_1 \right) \\
	&=: 4 (\alpha-1/2)^2 ( I_{11}(y_0) - I_{12}(y_0)). 
\end{align*}

@@

Next we compute $J_{a,b,c}(z_0)$.
\begin{align*}
	J_{a,b,c} 
	&= z_0^a \int_{z_0/2}^{z_0}\int_{z_0-z_1}^{z_1} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd}z_2{\dd}z_1
		= z_0^a \int_{z_0/2}^{z_0} z_1^{b+2\alpha-2} \left[ \frac{ z_2^{c+2\alpha-1} }{ c+2\alpha-1 } \right]_{z_0-z_1}^{z_1} \dd z_1\\
	&= \frac{z_0^a}{c+2\alpha-1} \cdot \left( \int_{z_0/2}^{z_0} z_1^{b+c+4\alpha-3} \dd z_1
	   - \int_{z_0/2}^{z_0} z_1^{b+2\alpha-2} (z_0-z_1)^{c+2\alpha-1} {\dd}z_1 \right) \\
	&= \frac{z_0^{a+b+c+4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} \\
	&\hspace{10pt}- \frac{z_0^{a+b+c+4\alpha-3}}{c+2\alpha-1} \int_{z_0/2}^{z_0}  \left(z_1/z_0\right)^{b+2\alpha-2} 
	    \left(1-(z_1/z_0)\right)^{c+2\alpha-1} \dd z_1\\
	&= \frac{z_0^{4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} 
		- \frac{z_0^{4\alpha-2}}{c+2\alpha-1}
	   \int_{1/2}^1  u^{b+2\alpha-2}(1-u)^{c+2\alpha-1} \dd u \\
	&= \frac{z_0^{4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} 
		- \frac{z_0^{4\alpha-2}}{c+2\alpha-1} B^-(1/2;c+2\alpha, b+2\alpha-1),
\end{align*}
where we've used the substitution $u := z_1/z_0$ giving $z_0 {\dd} u = {\dd} z_1$ in the penultimate line and
$B^-$ denotes the (lower) incomplete beta-function. Note that since $c \geq -1$, $-a \in \{0,-1,-2\}$ and by our assumption $\alpha \not \in \{\frac{3}{4},1\}$, the denominators that occur during the integration are all non-zero.

@@

We will follow a similar strategy as for $I_1(y_0)$. First, using the change of variables $z_i := e^{-y_i/2}$
we get
\begin{align*}
	I_2(y_0) &= 4 (\alpha-1/2)^2 \cdot \int_{1>z_1>z_2,z_0>0} P(y_0(z_0),y_1(z_1),y_2(z_2)) z_1^{2\alpha-2} z_2^{2\alpha-2} 
		{\dd}z_2{\dd}z_1 \\
	&= 4 (\alpha-1/2)^2 \cdot \left( \int_{1>z_1>z_0,z_2>0}  z_0 z_1^{2\alpha-3} z_2^{2\alpha-2} 
		{\dd}z_2{\dd}z_1 \right. \\
	&\hspace{10pt}\left. - \int_{{1>z_1>z_0,z_2>0}\atop{z_1 < z_0+z_2}} G(z_1,z_0,z_2) z_0 z_1^{2\alpha-3} 	
		z_2^{2\alpha-2} \dd z_2{\dd}z_1 \right) \\
	&=: 4 (\alpha-1/2)^2 (I_{21}(y_0) - I_{22}(y_0)). 
\end{align*}

@@

We know compute $J_{a,b,c}^\prime(z_0)$
\begin{align*}
	J_{a,b,c}^\prime(z_0) 
	&= z_0^a \int_{z_0}^1 \int_{z_1-z_0}^{z_1}  z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd} z_2 {\dd} z_1  \\
 	&= z_0^a \int_{z_0}^1 \frac{1}{c+2\alpha-1}  z_1^{b+2\alpha-2}( z_1^{c+2\alpha-1}-(z_1-z_0)^{c+2\alpha-1})  {\dd} z_1  \\
 	&=z_0^a \int_{z_0}^1 \frac{1}{c+2\alpha-1} z_1^{b+c+4\alpha-3} {\dd } z_1 -z_0^{a} \int_{z_0}^1 	
 		\frac{1}{c+2\alpha-1}z_1^{b+2\alpha-2}(z_1-z_0)^{c+2\alpha-1}  {\dd} z_1  \\
 	&= z_0^a  \frac{1}{(c+2\alpha-1)(b+c+4\alpha-2)}(1-z_0^{b+c+4\alpha-2}) \\
 	&\hspace{10pt}- \frac{z_0^a}{c+2\alpha-1}z_0^{b+c+4\alpha-2}B^-(1-z_0;c+2\alpha,-b-c-4\alpha+2) \\
	&= \frac{z_0^a -z_0^{4\alpha-2}}{(c+2\alpha-1)(b+c+4\alpha-2)}  
		- \frac{z_0^{4\alpha -2}B^-(1-z_0;c+2\alpha,-b-c-4\alpha+2)}{c+2\alpha-1}.  
\end{align*}
Here we used that for $x  \in \R,y>-1$ (note that as $c\geq -1$, it holds that $c+2\alpha-1 >-1$):
\begin{align*}
 \int_{z_0}^{1} z_1^x (z_1-z_0)^y {\dd} z_1 
 &= \int_0^{1-z_0} (s+z_0)^x s^y {\dd} s \\
 &= z_0^{x+y} \int_0^{1-z_0} \left( (s/z_0) + 1 \right)^x (s/z_0)^y {\dd} s \\
 &= z_0^{x+y+1} \int_{0}^{1/z_0 -1 } (t+1)^x t^y {\dd} t \\
 &= z_0^{x+y+1} \int_0^{1-z_0} u^y (1-u)^{-(x+y+2)} {\dd} u \\
 &= z_0^{x+y+1} B^-(1-z_0; y+1,-x-y-1 ).
\end{align*}
As $c \geq -1$ and $-a \in \{0,-1,-2\}$ and by our assumption $\alpha \not \in \{\frac{3}{4}\}$, the denominators 
that occur during the computations above are non-zero.

@@

Note that the factor $\alpha-\frac{3}{4}$ does not occur in any denominator of the previously obtained expression. 
For the lower incomplete beta function, the last argument $3-4\alpha$ is zero for $\alpha=\frac{3}{4}$, however as $z_0 < 1$ the 
integration domain of the lower incomplete beta function does not touch the singularity at $t=1$ 
(note $B^-(1-z_0;2\alpha;3-4\alpha) = \int_0^{1-z_0} t^{2\alpha-1} (1-t)^{2-4\alpha}$). 
Therefore, the previous expression holds for this case as well.

@@

We shall be assuming $\alpha \not = 1$. 
We observe from Lemma~\ref{lem:Paneq1} that for $\alpha \not =1$, $P(y(z))$ is in fact a linear combination 
of terms of the form $z^u$, $(1-z)^u$ and $z_0^u B^-(1-z_0,v,w)$.

>>>>

$$ \mu(y) = \mu(p) := \mu(\BallPo{p}). $$
Integrating the intensity function of $\Pcal$ over $\BallPo{p}$ gives, using $\alpha>\frac{1}{2}$,

@@

where $\Po(\lambda)$ denotes a Poisson random variable with expectation $\lambda$. 
We will often write $\rho(y,k)$ instead of $\rho(p,k)$.

Let the random variable $D$ denote the degree of the typical point.
Since the typical point has a height that is independent of the Poisson process and exponential($\alpha$)-distributed, for $k \in \N_0$:
\begin{equation}\label{eq:def_pk}
	p_k := \Pee( D=k ) = \int_0^\infty \rho(y,k) \alpha e^{-\alpha y} \, dy.
\end{equation}

@@

Let the random variable $C$ denote the clustering coefficient of the typical point $(0,y)$, in the graph obtained from $\Ginf$ by adding $(0,y)$. We {\em define}
\[
	\gamma := \Ee C, \quad \gamma(k) := \Ee\left( C | D = k \right).
\]
(Where we take the expectation over both the Poisson point process $\Pcal$ and $y \isd \text{exp}(\alpha)$, independently of the Poisson process $\Pcal$.) We shall show shortly that these take on the values stated in Theorem~\ref{thm:maincc} and~\ref{thm:mainkfixed}.

For any fixed value $y_0>0$, the set of points inside $\BallPo{(0,y_0)}$ is a Poisson process with intensity $f \cdot 1_{\BallPo{(0,y_0)}}$. As $\mu(\BallPo{(0,y_0)}) = \mu(y_0) = \xi e^{y_0/2} < \infty$, this can be described alternatively by the experiment where we first pick $N \isd \Po( \mu(y_0) )$ and then we take $N$ i.i.d.~points in $\BallPo{(0,y_0)}$ according to the probability density $f \cdot 1_{\BallPo{(0,y_0)}} / \mu(y_0)$. (That is, the intensity function of the Poisson point process, but set to zero outside of $\BallPo{(0,y_0)}$ and re-normalized in such a way that it integrates to one.) Hence, if we condition on the event that $y$ takes on some fixed value $y_0$ and that there are exactly $k$ points of $\Pcal$ inside $\BallPo{(0,y_0)}$, then those $k$ points behave like $k$ i.i.d.~points in $\BallPo{(0,y_0)}$ chosen according to the mentioned re-normalized probability density function. This shows that, for every $k\geq 2$:
\[
	\Ee\left( C | D=k, y=y_0 \right) 
	= \frac{1}{{k\choose 2}} \Ee\left( \sum_{1\leq i < j \leq k} \1_{\{u_i\in \BallPo{u_j}\}} \right)
	= \Exp{\1_{\{u_1\in\BallPo{u_2}\}}},
\]
where $u_1,\dots, u_n$ are i.i.d.~points in $\BallPo{(0,y_0)}$ with the above mentioned density.
Note that this does not depend on the value of $k$. For notational convenience, we will write 
\[ 
	P(y_0) := \Exp{\1_{\{u_1\in\BallPo{u_2}\}}},
\]
with $u_1, u_2$ as above.

@@

Recall that $P(y_0)$ is the probability that $u_1 = (x_1,y_1), u_2 = (x_2,y_2)$ are neighbours in $\Ginf$, where
$u_1, u_2$ are i.i.d.~with probability density $f \cdot \1_{\BallPo{(0,y_0)}} / \mu(y_0)$.
In particular

$$ \begin{array}{rcl} 
\Pee( y_i > t ) 
& = & 
\frac{\nu\alpha}{\pi \mu(y_0)} \int_t^\infty \int_{-e^{(s+y_0)/2}}^{e^{(s+y_0)/2}} e^{-\alpha s}\, d x \, d s \\
& = & 
\frac{\nu\alpha}{\pi \mu(y_0)} \int_t^\infty 2 e^{(s+y_0)/2} \cdot e^{-\alpha s}\, d s \\
& = & 
\frac{2 \nu\alpha e^{y_0/2} }{\pi \xi e^{y_0/2} (\alpha-\frac12) }  \cdot e^{(\frac12-\alpha)t} \\
& = & 
 e^{(\frac12-\alpha)t},
\end{array} $$

@@

\begin{lemma}\label{lem:triangle_prob_y_coordinates}
\begin{align*}
P(y_0(z_0),y_1(z_1),y_2(z_2)) = \begin{cases}
	1, &\text{ if } z_0 \geq z_1+z_2, z_0 > z_1 > z_2, \\
	1-G(z_0,z_1,z_2), &\text{ if } z_0 < z_1+z_2, z_0 > z_1 > z_2, \\
	\frac{z_0}{z_1}, &\text{ if } z_1 \geq z_0+z_2, z_1 > \max(z_0,z_2), \\
	\frac{z_0}{z_1}\left(1-G(z_1,z_0,z_2)\right), &\text{ if } z_1 < z_0+z_2, z_1 > \max(z_0,z_2),
\end{cases}
\end{align*}
where 
\begin{align*}
G(a,b,c) = \frac{1}{4}
\left( b^{-1}c + bc^{-1} + a^2b^{-1}c^{-1} + 2 - 2ab^{-1}-2ac^{-1}\right).
\end{align*}
\end{lemma}

@@

\begin{proof}
Note that $P(y_0,y_1,y_2)$ is the probability that $x_2$ falls into the interval $[x_1-e^{(y_1+y_2)/2},x_1+e^{(y_1+y_2)/2}]$, as well as into the interval $[-e^{(y_0+y_2)/2},e^{(y_0+y_2)/2}]$. By symmetry considerations, we can take $x_1$ uniformly at random from $[0,e^{y_0/2+y_1/2}]$ as opposed to $[-e^{y_0/2+y_1/2}, e^{y_0/2+y_1/2}]$. Figure~\ref{fig:triangle_prob_lemma} shows the intersection of the intervals (red line) for two different cases for $x_1 \le e^{(y_0 + y_1)/2}$.

@@

We now conclude that
\[
	P(y_0(z_0), y_1(z_1), y_2(z_2)) = 1 \quad \text{if} \quad z_0 > z_1 > z_2 \text{ and } z_0 \geq z_1 + z_2
\]
while for $z_0 > z_1 > z_2$ and $z_0 < z_1 + z_2$
\begin{align*}
	P(y_0(z_0), y_1(z_1), y_2(z_2)) 
	&= 1 - \frac{z_0^2z_1z_2}{4} \cdot \left( z_0^{-1}z_1^{-1}+z_0^{-1}z_2^{-1}-z_1^{-1}z_2^{-1} \right)^2 \\
%	&= 1 - \frac{z_0^2z_1z_2}{4} \cdot \left( z_0^{-2}z_1^{-2} + z_0^{-2}z_2^{-2} + z_1^{-2}z_2^{-2}
%		+ 2z_0^{-2}z_1^{-1}z_2^{-1} - 2 z_0^{-1}z_1^{-2}z_2^{-1} - 2z_0^{-1}z_1^{-1}z_2^{-2} \right) \\
	&= 1 - \frac{1}{4} \left( z_1^{-1}z_2 + z_1z_2^{-1} + z_0^2z_1^{-1}z_2^{-1} + 2 - 2z_0z_1^{-1}-2z_0z_2^{-1}\right),
\end{align*}
which finishes the proof.
\end{proof}

@@

\begin{proof}[Proof of Lemma~\ref{lem:triangle_prob_y_coordinates}]
Let $y_i >0$ and $z_i = e^{-y_i/2}$, $i=0,1,2$. Lemma~\ref{lem:ordered} gives the expression for $P(y_0(z_0),y_1(z_1),y_2(z_2))$ in the case $y_0<y_1<y_2$, or equivalently $z_0>z_1>z_2$, i.e. the first two lines in the claim of Lemma~\ref{lem:triangle_prob_y_coordinates}. To analyze the other cases we shall express $P(y_1,y_0,y_2)$ and $P(y_1,y_2,y_0)$ in terms of $P(y_0,y_1,y_2)$ and $z_i$. For this we note that we can view $P(y_0,y_1,y_2)$ as a 2-fold integral of the indicator function
\[ 
	h(x_0, x_1, x_2) := \ind{ |x_0 - x_1| < e^{(y_0+y_1)/2}, |x_0 - x_2| < e^{(y_0+y_2)/2}, |x_1-x_2| < e^{(y_1+y_2)/2}}, 
\]
where $x_0$ was set to zero, without loss of generality, and the other two $x_i$ are uniform random variables on $[-e^{(y_0+y_i)/2}, e^{(y_0+y_i)/2}]$. When we consider the probability $P(y_1,y_0,y_2)$, this is the 2-fold integral of $h(x_0,0,x_2)$ so that
\begin{align*}
	P(y_1,y_0,y_2) &= \frac{1}{2e^{(y_1+y_0)/2}} \cdot \frac{1}{2e^{(y_1+y_2)/2}} 
		\iint_{\R} h(x_0,0,x_2) \dd x_0 \dd x_2\\
	&= \frac{e^{y_0/2}}{e^{y_1/2}} \frac{1}{2e^{(y_0+y_1)/2}} \frac{1}{2e^{(y_0+y_2)/2}} 
		\iint_{\R} h(0,x_1,x_2) \dd x_1 \dd x_2\\
	&= \frac{e^{y_0/2}}{e^{y_1/2}} P(y_0,y_1,y_2) = \frac{z_1}{z_0}  P(y_0,y_1,y_2).
\end{align*}
Finally we note that $h(x_0,0,x_2) = h(x_2,0,x_0)$ from which we conclude that
\begin{equation}\label{eq:symmetry_relation_triangle_prob}
	P(y_0, y_1, y_2) = \left(z_0/z_1\right) P(y_1,y_0,y_2) = \left(z_0/z_1\right) P(y_1,y_2,y_0).
\end{equation}

@@

Applying the change of variables $z_i := e^{-y_i/2}$, $i=1,2$, and Lemma~\ref{lem:triangle_prob_y_coordinates} gives %${\dd}y_i = -\frac{2{\dd}z_i}{z_i}$ and therefore
\begin{align*}
	I_1(y_0) &=	4 (\alpha-1/2)^2 \cdot \int_{z_0>z_1>z_2>0} P(y_0,y_1(z),y_2(z)) z_1^{2\alpha-2} z_2^{2\alpha-2} 
		{\dd}z_2{\dd}z_1 \\
	&= 4 (\alpha-1/2)^2 \cdot \left( \int_{z_0>z_1>z_2>0} 1 \cdot z_1^{2\alpha-2} z_2^{2\alpha-2} 
		{\dd}z_2{\dd}z_1 \right. \\
	&\hspace{10pt} \left. - \int_{{z_0>z_1>z_2>0,}\atop{z_0 < z_1+z_2}} G(z_0,z_1,z_2) \cdot z_1^{2\alpha-2} z_2^{2\alpha-2} 
		{\dd}z_2{\dd}z_1 \right) \\
	&=: 4 (\alpha-1/2)^2 ( I_{11}(y_0) - I_{12}(y_0)). 
\end{align*}

@@

Next we compute $J_{a,b,c}(z_0)$.
\begin{align*}
	J_{a,b,c}(z_0) 
	&= z_0^a \int_{z_0/2}^{z_0}\int_{z_0-z_1}^{z_1} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd}z_2{\dd}z_1
		= z_0^a \int_{z_0/2}^{z_0} z_1^{b+2\alpha-2} \left[ \frac{ z_2^{c+2\alpha-1} }{ c+2\alpha-1 } \right]_{z_0-z_1}^{z_1} \dd z_1\\
	&= \frac{z_0^a}{c+2\alpha-1} \cdot \left( \int_{z_0/2}^{z_0} z_1^{b+c+4\alpha-3} \dd z_1
	   - \int_{z_0/2}^{z_0} z_1^{b+2\alpha-2} (z_0-z_1)^{c+2\alpha-1} {\dd}z_1 \right) \\
	&= \frac{z_0^{a+b+c+4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} \\
	&\hspace{10pt}- \frac{z_0^{a+b+c+4\alpha-3}}{c+2\alpha-1} \int_{z_0/2}^{z_0}  \left(z_1/z_0\right)^{b+2\alpha-2} 
	    \left(1-(z_1/z_0)\right)^{c+2\alpha-1} \dd z_1\\
	&= \frac{z_0^{4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} 
		- \frac{z_0^{4\alpha-2}}{c+2\alpha-1}
	   \int_{1/2}^1  u^{b+2\alpha-2}(1-u)^{c+2\alpha-1} \dd u \\
	&= \frac{z_0^{4\alpha-2}(1-(1/2)^{b+c+4\alpha-2})}{(c+2\alpha-1)(b+c+4\alpha-2)} 
		- \frac{z_0^{4\alpha-2}}{c+2\alpha-1} B^-(1/2;c+2\alpha, b+2\alpha-1),
\end{align*}
where we have used the substitution $u := z_1/z_0$ giving $z_0 {\dd} u = {\dd} z_1$ in the penultimate line and
$B^-$ denotes the (lower) incomplete beta function. Note that since $c \geq -1$, $-a \in \{0,-1,-2\}$ and by our assumption $\alpha \not \in \{\frac{3}{4},1\}$, the denominators that occur during the integration are all non-zero.

@@

We will follow a similar strategy as for $I_1(y_0)$. First, using the change of variables $z_i := e^{-y_i/2}$, $i=1,2$,
we get
\begin{align*}
	I_2(y_0) &= 4 (\alpha-1/2)^2 \cdot \int_{1>z_1>z_2,z_0>0} P(y_0,y_1(z_1),y_2(z_2)) z_1^{2\alpha-2} z_2^{2\alpha-2} 
		{\dd}z_2{\dd}z_1 \\
	&= 4 (\alpha-1/2)^2 \cdot \left( \int_{1>z_1>z_0,z_2>0}  z_0 z_1^{2\alpha-3} z_2^{2\alpha-2} 
		{\dd}z_2{\dd}z_1 \right. \\
	&\hspace{10pt}\left. - \int_{{1>z_1>z_0,z_2>0}\atop{z_1 < z_0+z_2}} G(z_1,z_0,z_2) z_0 z_1^{2\alpha-3} 	
		z_2^{2\alpha-2} \dd z_2{\dd}z_1 \right) \\
	&=: 4 (\alpha-1/2)^2 (I_{21}(y_0) - I_{22}(y_0)). 
\end{align*}

@@

We now compute $J_{a,b,c}^\prime(z_0)$
\begin{align*}
	J_{a,b,c}^\prime(z_0) 
	&= z_0^a \int_{z_0}^1 \int_{z_1-z_0}^{z_1}  z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd} z_2 {\dd} z_1  \\
 	&= z_0^a \int_{z_0}^1 \frac{1}{c+2\alpha-1}  z_1^{b+2\alpha-2}( z_1^{c+2\alpha-1}-(z_1-z_0)^{c+2\alpha-1})  {\dd} z_1  \\
 	&=z_0^a \int_{z_0}^1 \frac{1}{c+2\alpha-1} z_1^{b+c+4\alpha-3} {\dd } z_1 -z_0^{a} \int_{z_0}^1 	
 		\frac{1}{c+2\alpha-1}z_1^{b+2\alpha-2}(z_1-z_0)^{c+2\alpha-1}  {\dd} z_1  \\
 	&= z_0^a  \frac{1}{(c+2\alpha-1)(b+c+4\alpha-2)}(1-z_0^{b+c+4\alpha-2}) \\
 	&\hspace{10pt}- \frac{z_0^a}{c+2\alpha-1}z_0^{b+c+4\alpha-2}B^-(1-z_0;c+2\alpha,-b-c-4\alpha+2) \\
	&= \frac{z_0^a -z_0^{4\alpha-2}}{(c+2\alpha-1)(b+c+4\alpha-2)}  
		- \frac{z_0^{4\alpha -2}B^-(1-z_0;c+2\alpha,-b-c-4\alpha+2)}{c+2\alpha-1}.  
\end{align*}
Here we used that for $x  \in \R,y>-1$ (note that as $c\geq -1$, it holds that $c+2\alpha-1 >-1$):
\begin{align*}
 \int_{z_0}^{1} z_1^x (z_1-z_0)^y {\dd} z_1 
 &= \int_0^{1-z_0} (s+z_0)^x s^y {\dd} s \\
 &= z_0^{x+y} \int_0^{1-z_0} \left( (s/z_0) + 1 \right)^x (s/z_0)^y {\dd} s \\
 &= z_0^{x+y+1} \int_{0}^{1/z_0 -1 } (t+1)^x t^y {\dd} t \\
 &= z_0^{x+y+1} \int_0^{1-z_0} u^y (1-u)^{-(x+y+2)} {\dd} u \\
 &= z_0^{x+y+1} B^-(1-z_0; y+1,-x-y-1 ).
\end{align*}
As $c \geq -1$ and $-a \in \{0,-1,-2\}$ and by our assumption $\alpha \not \in \{\frac{3}{4}\}$, the denominators 
that occur during the computations above are non-zero.

@@

Note that the factor $\alpha-\frac{3}{4}$ does not occur in any denominator of the previously obtained expression. 
For the lower incomplete beta function, the last argument $3-4\alpha$ is zero for $\alpha=\frac{3}{4}$, however as $z_0 < 1$ the 
integration domain of the lower incomplete beta function does not touch the singularity at $t=1$ 
(note $B^-(1-z_0;2\alpha,3-4\alpha) = \int_0^{1-z_0} t^{2\alpha-1} (1-t)^{2-4\alpha}dt$). 
Therefore, the previous expression holds for this case as well.

@@

We shall be assuming $\alpha \not = 1$. 
We observe from Lemma~\ref{lem:Paneq1} that for $\alpha \not =1$, $P(y(z))$ is in fact a linear combination 
of terms of the form $z^u$, $(1-z)^u$ and $z^u B^-(1-z;v,w)$.
